A / B test

### 2016-01-06 3_AB_test/AB_test.Rmd
AB test 2

---
title: "A / B test"
author: "Ming-Yu Liu"
date: "January 11, 2016"
output: 
  html_document: 
    highlight: pygments
    number_sections: yes
    theme: cosmo
    toc: yes
---

@@

Suppose you're running an educational platform and your hypothesis is : Will changing the "Start Now" button from orange to pink increase how many students explore the platform's courses. So in this case the metric that's use to evaluate the change's performance is the click through probability ( Unique visitors who click the button / Unique visitors to page ). Note that it is often times impractical to use metrices such as total number of students that completed the course as it often takes weeks or months before a student can do that.

@@

confidence <- ABTest( count_control = count_control, 
					  sizes_control = sizes_control,
					  count_experiment = count_experiment, 
					  sizes_experiment = sizes_experiment )

@@

In order to launch a change, the change should be larger than the minimum detectable change that you wished to detect, or in other words it should be larger than your practical significance boundary. In our case, the value we've set was `r delta`. From the result above, we can denote that since even the lower bound of the confidence interval is larger than the value. Base on this fact, we'll definitely launch the newer version of the click button.

@@

scenario <- as.character(2:6)
lower <- c( -0.008, 0.01, -0.025, -0.005, 0.015   )
mean  <- c( 0.01, 0.015, 0.005, 0.025, 0.025 )
upper <- c( 0.018, 0.018, 0.03, 0.04, 0.03 )

@@

@@

Source [code](https://github.com/ethen8181/machine-learning/blob/master/3_AB_test/AB_test.R) to the documentation.

Bugs are comments can be filed [here](https://github.com/ethen8181/Business-Analytics/issues).

@@

[ABTest]: https://github.com/ethen8181/machine-learning/blob/master/3_AB_test/AB_test.R

>>>>

---
title: "A / B test"
author: "Ming-Yu Liu"
date: "January 11, 2016"
output: 
  html_document: 
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

@@

So now, suppose you're running an educational platform and your hypothesis is : Will changing the "Start Now" button from orange to pink increase how many students explore the platform's courses. So in this case the metric that's use to evaluate the change's performance is the click through probability ( Unique visitors who click the button / Unique visitors to page ). Note that it is often times impractical to use metrices such as total number of students that completed the course as it often takes weeks or months before a student can do that.

@@

confidence <- ABTest( count_control = count_control, 
					  sizes_control = sizes_control,
					  count_experiment = count_experiment, 
					  sizes_experiment = sizes_experiment )
confidence

@@

In order to launch a change, the change should be larger than the minimum detectable change that you wished to detect, or in other words it should be larger than your practical significance boundary. In our case, the value we've set was `r delta`. Base on the result above, we can denote that since even the lower bound of the confidence interval is larger than the value, we'll definitely launch the newer version of the click button.

@@

scenario <- as.character(2:6)
lower <- c( -0.008, 0.011, -0.025, -0.005, 0.015 )
mean  <- c( 0.005, 0.014, 0.005, 0.025, 0.025 )
upper <- c( 0.018, 0.017, 0.035, 0.055, 0.035 )

@@

## Characterizing a Proper Metric

After seeing an simple A / B test example, we'll take a step back and see how do come up with a well-defined metric.

**Step1: Generate a high level metrices**

A non-exhaustive list of techniques that might be able to help you come up with high level metrices that you might want to test out in your experiment.

1. External Sources : For these types of data, do not *match* them with internal data that you might already have at hand. Instead, look at a time series of both your
internally computed metric and the externally available one and see if the trends and seasonal variability line up.
2. Gathering your own data : 
    - User Experience Group.
    - Focus Group.
    - Retrospective Analysis.
    - Survey.

**Step2: Turning it into a well-defined metrices**

Recall that in the examples above, we've chosen the high-level metric click-through probability. And this is defined by the unique number of people how click the button versus the number of users who visited the home page.

But to actually use implement the definition, we'll also have to address some other questions. Such as : If the same user visits the page once and comes back a week or two later, do we still only want to count that once? Usually, it is preferred that we count these separately, thus we'll also need to specify a time period.

So given that users are usually recorded by cookies online. One version of the fully-defined metric will be : For each minute ( choose any time interval that you prefer ), the number of cookies that clicked divided by the number of cookies that interacted with the page.

Another way of implementing this is to calculate : For each minute the number of pageviews ( assign each pageview with an id ) with a click divided by the number of pageviews.

**Step3: Segmenting and filtering your traffic**

Creating segments and filtering out data can be useful for evaluating metric definitions, because, well, you can look at how the different definitions vary by segment.

For example, you're looking at your metric of total active cookie users over time. And you see a spike in one of the timelines. After confirming that this is not caused by seasonal variation, we can look at different segment of our visitors to see if one of the segment is causing the spike.

Suppose we have chosen segment to be platforms ( mobile and desktop ). Plot the rate and probability by platforms to determine

## Others

Some principles to consider when designing A / B test :

1. Risk : What risk is the participant undertaking? The main threshold is whether the risk exceeds that of “minimal risk”. e.g. people's health.
2. Benefits : What benefits might result from the study?
3. Alternatives : What other choices do people have? In a sense are the people coerced to participate since they lack other alternatives to choose from.
4. Data Sensitivity : What level of confidentiality can participants expect? Studies without personal data like names or simply data that can't be match to an individual are generally fine. Though a terms of service or a privacy policy is necessary, as it contains a clear statement of what data are you going to collect and how you use it.

@@

Source [code](https://github.com/ethen8181/Business-Analytics/blob/master/3_AB_test/AB_test.R) to the documentation.

Bugs or comments can be filed [here](https://github.com/ethen8181/Business-Analytics/issues).

@@

[ABTest]: https://github.com/ethen8181/Business-Analytics/blob/master/3_AB_test/AB_test.R
